Probing internal structure of distant quasars using Microlensing

### 2014-03-27 paper1/ms.tex
code.tex added
Edits from Mihai
whatever
re-arranged by Irshad
minor

\documentclass[usenatbib,twocolumn]{mn2e}

@@

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^3$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

\input{sourcemodels}

>>>>

\documentclass[usenatbib,onecolumn]{mn2e}

@@

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

\input{code}
